Measuring the Price of Anarchy in Critical Care Unit Interactions

### 2014-12-09 Paper/paper.tex
Have updated graph for new labelling of regions

\begin{figure}[!htbp]
\begin{center}
    \begin{tikzpicture}[scale=.7, every node/.style={scale=0.7}]
        % -----------------------------------------------
        % Boundaries ------------------------------------
        % -----------------------------------------------
        \draw [dashed, line width=1mm, red, opacity=.3] (12,2) -- (12,-20);
        \draw [dashed, line width=1mm, red, opacity=.3] (-2,-12) -- (20,-12);
        %\tikzstyle{state}=[ellipse, draw, fill=blue!10, minimum width=2cm];
        %\tikzstyle{state}=[rectangle, draw, fill=blue!10, minimum width=2cm];
        \tikzstyle{state}=[minimum width=2cm, font=\boldmath];
        %\draw  (0,0) rectangle (4,3);
        %\draw [dashed, red, thick] (0,1) -- (4,1);
        %\draw [dashed, red, thick] (3,0) -- (3,3);
        % -----------------------------------------------
        % First row--------------------------------------
        % -----------------------------------------------
        \node (aa) [state] at (0,0) {$(0,0)$};
        \node (ab) [state] at ($(aa) + (3,0)$) {$(0,1)$};
        \node (ac) [state] at ($(ab) + (3,0)$) {$(0,2)$};
        \node (ellipsisa1) at ($(ac) + (3,0)$) {$\dots$};
        \node(ak) [state] at ($(ellipsisa1) + (3,0)$) {$(0,K_{\RG})$};
        \node (ellipsisa2) at ($(ak) + (3,0)$) {$\dots$};
        \node(az) [state] at ($(ellipsisa2) + (3,0)$) {$(0,c_{\RG})$};
        % Transitions -----------------------------------
        % On Row:
        \draw (aa) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(a)}$} (ab);
        \draw (aa) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$\mu_{\RG}$} (ab);

        \draw (ab) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(a)}$} (ac);
        \draw (ab) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$2\mu_{\RG}$} (ac);

        \draw (ac) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(a)}$} (ellipsisa1);
        \draw (ac) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$3\mu_{\RG}$} (ellipsisa1);

        \draw (ellipsisa1) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(a)}$} (ak);
        \draw (ellipsisa1) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$K_{\RG}\mu_{\RG}$} (ak);

        \draw (ak) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(b)}$} (ellipsisa2);
        \draw (ak) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$(K_{\RG}+1)\mu_{\RG}$} (ellipsisa2);

        \draw (ellipsisa2) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(b)}$} (az);
        \draw (ellipsisa2) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$c_{\RG}\mu_{\RG}$} (az);
        % -----------------------------------------------
        % Second row--------------------------------------
        % -----------------------------------------------
        \node (ba) [state] at (0,-3) {$(1,0)$};
        \node (bb) [state] at ($(ba) + (3,0)$) {$(1,1)$};
        \node (bc) [state] at ($(bb) + (3,0)$) {$(1,2)$};
        \node (ellipsisb1) at ($(bc) + (3,0)$) {$\dots$};
        \node(bk) [state] at ($(ellipsisb1) + (3,0)$) {$(1,K_{\RG})$};
        \node (ellipsisb2) at ($(bk) + (3,0)$) {$\dots$};
        \node(bz) [state] at ($(ellipsisb2) + (3,0)$) {$(1,c_{\RG})$};
        % Transitions -----------------------------------
        % On Row:
        \draw (ba) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(a)}$} (bb);
        \draw (ba) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$\mu_{\RG}$} (bb);

        \draw (bb) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(a)}$} (bc);
        \draw (bb) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$2\mu_{\RG}$} (bc);

        \draw (bc) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(a)}$} (ellipsisb1);
        \draw (bc) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$333\mu_{\RG}$} (ellipsisb1);

        \draw (ellipsisb1) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(a)}$} (bk);
        \draw (ellipsisb1) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$K_{\RG}\mu_{\RG}$} (bk);

        \draw (bk) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(b)}$} (ellipsisb2);
        \draw (bk) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$(K_{\RG} + 1)\mu_{\RG}$} (ellipsisb2);

        \draw (ellipsisb2) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(b)}$} (bz);
        \draw (ellipsisb2) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$c_{\RG}\mu_{\RG}$} (bz);
        % With previous row:
        \draw (aa) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(a)}$} (ba);
        \draw (aa) edge[out=-55,in=55,<-,thick] node [right] {\tiny$\mu_{\NH}$} (ba);

        \draw (ab) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(a)}$} (bb);
        \draw (ab) edge[out=-55,in=55,<-,thick] node [right] {\tiny$\mu_{\NH}$} (bb);

        \draw (ac) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(a)}$} (bc);
        \draw (ac) edge[out=-55,in=55,<-,thick] node [right] {\tiny$\mu_{\NH}$} (bc);

        \draw (ellipsisa1) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(a)}$} (ellipsisb1);
        \draw (ellipsisa1) edge[out=-55,in=55,<-,thick] node [right] {\tiny$\mu_{\NH}$} (ellipsisb1);

        \draw (ak) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(b)}$} (bk);
        \draw (ak) edge[out=-55,in=55,<-,thick] node [right] {\tiny$\mu_{\NH}$} (bk);

        \draw (ellipsisa2) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(b)}$} (ellipsisb2);
        \draw (ellipsisa2) edge[out=-55,in=55,<-,thick] node [right] {\tiny$\mu_{\NH}$} (ellipsisb2);

        \draw (az) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(b)}$} (bz);
        \draw (az) edge[out=-55,in=55,<-,thick] node [right] {\tiny$\mu_{\NH}$} (bz);
        % -----------------------------------------------
        % Third row--------------------------------------
        % -----------------------------------------------
        \node (ca) [state] at (0,-6) {$(2,0)$};
        \node (cb) [state] at ($(ca) + (3,0)$) {$(2,1)$};
        \node (cc) [state] at ($(cb) + (3,0)$) {$(2,2)$};
        \node (ellipsisc1) at ($(cc) + (3,0)$) {$\dots$};
        \node(ck) [state] at ($(ellipsisc1) + (3,0)$) {$(2,K_{\RG})$};
        \node (ellipsisc2) at ($(ck) + (3,0)$) {$\dots$};
        \node(cz) [state] at ($(ellipsisc2) + (3,0)$) {$(2,c_{\RG})$};
        % Transitions -----------------------------------
        % On Row:
        \draw (ca) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(a)}$} (cb);
        \draw (ca) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$\mu_{\RG}$} (cb);

        \draw (cb) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(a)}$} (cc);
        \draw (cb) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$2\mu_{\RG}$} (cc);

        \draw (cc) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(a)}$} (ellipsisc1);
        \draw (cc) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$333\mu_{\RG}$} (ellipsisc1);

        \draw (ellipsisc1) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(a)}$} (ck);
        \draw (ellipsisc1) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$K_{\RG}\mu_{\RG}$} (ck);

        \draw (ck) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(b)}$} (ellipsisc2);
        \draw (ck) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$(K_{\RG} + 1)\mu_{\RG}$} (ellipsisc2);

        \draw (ellipsisc2) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(b)}$} (cz);
        \draw (ellipsisc2) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$c_{\RG}\mu_{\RG}$} (cz);
        % With previous row:
        \draw (ba) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(a)}$} (ca);
        \draw (ba) edge[out=-55,in=55,<-,thick] node [right] {\tiny$2\mu_{\NH}$} (ca);

        \draw (bb) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(a)}$} (cb);
        \draw (bb) edge[out=-55,in=55,<-,thick] node [right] {\tiny$2\mu_{\NH}$} (cb);

        \draw (bc) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(a)}$} (cc);
        \draw (bc) edge[out=-55,in=55,<-,thick] node [right] {\tiny$2\mu_{\NH}$} (cc);

        \draw (ellipsisb1) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(a)}$} (ellipsisc1);
        \draw (ellipsisb1) edge[out=-55,in=55,<-,thick] node [right] {\tiny$2\mu_{\NH}$} (ellipsisc1);

        \draw (bk) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(b)}$} (ck);
        \draw (bk) edge[out=-55,in=55,<-,thick] node [right] {\tiny$2\mu_{\NH}$} (ck);

        \draw (ellipsisb2) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(b)}$} (ellipsisc2);
        \draw (ellipsisb2) edge[out=-55,in=55,<-,thick] node [right] {\tiny$2\mu_{\NH}$} (ellipsisc2);

        \draw (bz) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(b)}$} (cz);
        \draw (bz) edge[out=-55,in=55,<-,thick] node [right] {\tiny$\mu_{\NH}$} (cz);
        % -----------------------------------------------
        % Fourth row--------------------------------------
        % -----------------------------------------------
        \node (da) at (0,-9) {$\vdots$};
        \node (db) at ($(da) + (3,0)$) {$\vdots$};
        \node (dc) at ($(db) + (3,0)$) {$\vdots$};
        \node (ellipsisd1) at ($(dc) + (3,0)$) {$\dots$};
        \node(dk) at ($(ellipsisd1) + (3,0)$) {$\vdots$};
        \node (ellipsisd2) at ($(dk) + (3,0)$) {$\dots$};
        \node(dz) at ($(ellipsisd2) + (3,0)$) {$\vdots$};
        % Transitions -----------------------------------
        % On Row:
        \draw (da) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(a)}$} (db);
        \draw (da) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$\mu_{\RG}$} (db);

        \draw (db) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(a)}$} (dc);
        \draw (db) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$2\mu_{\RG}$} (dc);

        \draw (dc) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(a)}$} (ellipsisd1);
        \draw (dc) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$333\mu_{\RG}$} (ellipsisd1);

        \draw (ellipsisd1) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(a)}$} (dk);
        \draw (ellipsisd1) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$K_{\RG}\mu_{\RG}$} (dk);

        \draw (dk) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(b)}$} (ellipsisd2);
        \draw (dk) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$(K_{\RG} + 1)\mu_{\RG}$} (ellipsisd2);

        \draw (ellipsisd2) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(b)}$} (dz);
        \draw (ellipsisd2) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$c_{\RG}\mu_{\RG}$} (dz);
        % With previous row:
        \draw (ca) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(a)}$} (da);
        \draw (ca) edge[out=-55,in=55,<-,thick] node [right] {\tiny$3\mu_{\NH}$} (da);

        \draw (cb) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(a)}$} (db);
        \draw (cb) edge[out=-55,in=55,<-,thick] node [right] {\tiny$3\mu_{\NH}$} (db);

        \draw (cc) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(a)}$} (dc);
        \draw (cc) edge[out=-55,in=55,<-,thick] node [right] {\tiny$3\mu_{\NH}$} (dc);

        \draw (ellipsisc1) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(a)}$} (ellipsisd1);
        \draw (ellipsisc1) edge[out=-55,in=55,<-,thick] node [right] {\tiny$3\mu_{\NH}$} (ellipsisd1);

        \draw (ck) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(b)}$} (dk);
        \draw (ck) edge[out=-55,in=55,<-,thick] node [right] {\tiny$3\mu_{\NH}$} (dk);

        \draw (ellipsisc2) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(b)}$} (ellipsisd2);
        \draw (ellipsisc2) edge[out=-55,in=55,<-,thick] node [right] {\tiny$3\mu_{\NH}$} (ellipsisd2);

        \draw (cz) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(b)}$} (dz);
        \draw (cz) edge[out=-55,in=55,<-,thick] node [right] {\tiny$\mu_{\NH}$} (dz);
        % -----------------------------------------------
        % Fifth row--------------------------------------
        % -----------------------------------------------
        \node (ea) [state] at (0,-12) {$(K_{\NH},0)$};
        \node (eb) [state] at ($(ea) + (3,0)$) {$(K_{\NH},1)$};
        \node (ec) [state] at ($(eb) + (3,0)$) {$(K_{\NH},2)$};
        \node (ellipsise1) at ($(ec) + (3,0)$) {$\dots$};
        \node(ek) [state] at ($(ellipsise1) + (3,0)$) {$(K_{\NH},K_{\RG})$};
        \node (ellipsise2) at ($(ek) + (3,0)$) {$\dots$};
        \node(ez) [state] at ($(ellipsise2) + (3,0)$) {$(K_{\NH},c_{\RG})$};
        % Transitions -----------------------------------
        % On Row:
        \draw (ea) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(c)}$} (eb);
        \draw (ea) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$\mu_{\RG}$} (eb);

        \draw (eb) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(c)}$} (ec);
        \draw (eb) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$2\mu_{\RG}$} (ec);

>>>>

\begin{figure}[!htbp]
\begin{center}
    \begin{tikzpicture}[scale=.7, every node/.style={scale=0.7}]
        % -----------------------------------------------
        % Boundaries ------------------------------------
        % -----------------------------------------------
        \draw [dashed, line width=1mm, red, opacity=.3] (12,2) -- (12,-20);
        \draw [dashed, line width=1mm, red, opacity=.3] (-2,-12) -- (20,-12);
        %\tikzstyle{state}=[ellipse, draw, fill=blue!10, minimum width=2cm];
        %\tikzstyle{state}=[rectangle, draw, fill=blue!10, minimum width=2cm];
        \tikzstyle{state}=[minimum width=2cm, font=\boldmath];
        %\draw  (0,0) rectangle (4,3);
        %\draw [dashed, red, thick] (0,1) -- (4,1);
        %\draw [dashed, red, thick] (3,0) -- (3,3);
        % -----------------------------------------------
        % First row--------------------------------------
        % -----------------------------------------------
        \node (aa) [state] at (0,0) {$(0,0)$};
        \node (ab) [state] at ($(aa) + (3,0)$) {$(0,1)$};
        \node (ac) [state] at ($(ab) + (3,0)$) {$(0,2)$};
        \node (ellipsisa1) at ($(ac) + (3,0)$) {$\dots$};
        \node(ak) [state] at ($(ellipsisa1) + (3,0)$) {$(0,K_{\RG})$};
        \node (ellipsisa2) at ($(ak) + (3,0)$) {$\dots$};
        \node(az) [state] at ($(ellipsisa2) + (3,0)$) {$(0,c_{\RG})$};
        % Transitions -----------------------------------
        % On Row:
        \draw (aa) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(l,l)}$} (ab);
        \draw (aa) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$\mu_{\RG}$} (ab);

        \draw (ab) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(l,l)}$} (ac);
        \draw (ab) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$2\mu_{\RG}$} (ac);

        \draw (ac) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(l,l)}$} (ellipsisa1);
        \draw (ac) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$3\mu_{\RG}$} (ellipsisa1);

        \draw (ellipsisa1) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(l,l)}$} (ak);
        \draw (ellipsisa1) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$K_{\RG}\mu_{\RG}$} (ak);

        \draw (ak) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(l,h)}$} (ellipsisa2);
        \draw (ak) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$(K_{\RG}+1)\mu_{\RG}$} (ellipsisa2);

        \draw (ellipsisa2) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(l,h)}$} (az);
        \draw (ellipsisa2) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$c_{\RG}\mu_{\RG}$} (az);
        % -----------------------------------------------
        % Second row--------------------------------------
        % -----------------------------------------------
        \node (ba) [state] at (0,-3) {$(1,0)$};
        \node (bb) [state] at ($(ba) + (3,0)$) {$(1,1)$};
        \node (bc) [state] at ($(bb) + (3,0)$) {$(1,2)$};
        \node (ellipsisb1) at ($(bc) + (3,0)$) {$\dots$};
        \node(bk) [state] at ($(ellipsisb1) + (3,0)$) {$(1,K_{\RG})$};
        \node (ellipsisb2) at ($(bk) + (3,0)$) {$\dots$};
        \node(bz) [state] at ($(ellipsisb2) + (3,0)$) {$(1,c_{\RG})$};
        % Transitions -----------------------------------
        % On Row:
        \draw (ba) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(l,l)}$} (bb);
        \draw (ba) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$\mu_{\RG}$} (bb);

        \draw (bb) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(l,l)}$} (bc);
        \draw (bb) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$2\mu_{\RG}$} (bc);

        \draw (bc) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(l,l)}$} (ellipsisb1);
        \draw (bc) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$333\mu_{\RG}$} (ellipsisb1);

        \draw (ellipsisb1) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(l,l)}$} (bk);
        \draw (ellipsisb1) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$K_{\RG}\mu_{\RG}$} (bk);

        \draw (bk) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(l,h)}$} (ellipsisb2);
        \draw (bk) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$(K_{\RG} + 1)\mu_{\RG}$} (ellipsisb2);

        \draw (ellipsisb2) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(l,h)}$} (bz);
        \draw (ellipsisb2) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$c_{\RG}\mu_{\RG}$} (bz);
        % With previous row:
        \draw (aa) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(l,l)}$} (ba);
        \draw (aa) edge[out=-55,in=55,<-,thick] node [right] {\tiny$\mu_{\NH}$} (ba);

        \draw (ab) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(l,l)}$} (bb);
        \draw (ab) edge[out=-55,in=55,<-,thick] node [right] {\tiny$\mu_{\NH}$} (bb);

        \draw (ac) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(l,l)}$} (bc);
        \draw (ac) edge[out=-55,in=55,<-,thick] node [right] {\tiny$\mu_{\NH}$} (bc);

        \draw (ellipsisa1) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(l,l)}$} (ellipsisb1);
        \draw (ellipsisa1) edge[out=-55,in=55,<-,thick] node [right] {\tiny$\mu_{\NH}$} (ellipsisb1);

        \draw (ak) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(l,h)}$} (bk);
        \draw (ak) edge[out=-55,in=55,<-,thick] node [right] {\tiny$\mu_{\NH}$} (bk);

        \draw (ellipsisa2) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(l,h)}$} (ellipsisb2);
        \draw (ellipsisa2) edge[out=-55,in=55,<-,thick] node [right] {\tiny$\mu_{\NH}$} (ellipsisb2);

        \draw (az) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(l,h)}$} (bz);
        \draw (az) edge[out=-55,in=55,<-,thick] node [right] {\tiny$\mu_{\NH}$} (bz);
        % -----------------------------------------------
        % Third row--------------------------------------
        % -----------------------------------------------
        \node (ca) [state] at (0,-6) {$(2,0)$};
        \node (cb) [state] at ($(ca) + (3,0)$) {$(2,1)$};
        \node (cc) [state] at ($(cb) + (3,0)$) {$(2,2)$};
        \node (ellipsisc1) at ($(cc) + (3,0)$) {$\dots$};
        \node(ck) [state] at ($(ellipsisc1) + (3,0)$) {$(2,K_{\RG})$};
        \node (ellipsisc2) at ($(ck) + (3,0)$) {$\dots$};
        \node(cz) [state] at ($(ellipsisc2) + (3,0)$) {$(2,c_{\RG})$};
        % Transitions -----------------------------------
        % On Row:
        \draw (ca) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(l,l)}$} (cb);
        \draw (ca) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$\mu_{\RG}$} (cb);

        \draw (cb) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(l,l)}$} (cc);
        \draw (cb) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$2\mu_{\RG}$} (cc);

        \draw (cc) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(l,l)}$} (ellipsisc1);
        \draw (cc) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$333\mu_{\RG}$} (ellipsisc1);

        \draw (ellipsisc1) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(l,l)}$} (ck);
        \draw (ellipsisc1) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$K_{\RG}\mu_{\RG}$} (ck);

        \draw (ck) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(l,h)}$} (ellipsisc2);
        \draw (ck) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$(K_{\RG} + 1)\mu_{\RG}$} (ellipsisc2);

        \draw (ellipsisc2) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(l,h)}$} (cz);
        \draw (ellipsisc2) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$c_{\RG}\mu_{\RG}$} (cz);
        % With previous row:
        \draw (ba) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(l,l)}$} (ca);
        \draw (ba) edge[out=-55,in=55,<-,thick] node [right] {\tiny$2\mu_{\NH}$} (ca);

        \draw (bb) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(l,l)}$} (cb);
        \draw (bb) edge[out=-55,in=55,<-,thick] node [right] {\tiny$2\mu_{\NH}$} (cb);

        \draw (bc) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(l,l)}$} (cc);
        \draw (bc) edge[out=-55,in=55,<-,thick] node [right] {\tiny$2\mu_{\NH}$} (cc);

        \draw (ellipsisb1) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(l,l)}$} (ellipsisc1);
        \draw (ellipsisb1) edge[out=-55,in=55,<-,thick] node [right] {\tiny$2\mu_{\NH}$} (ellipsisc1);

        \draw (bk) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(l,h)}$} (ck);
        \draw (bk) edge[out=-55,in=55,<-,thick] node [right] {\tiny$2\mu_{\NH}$} (ck);

        \draw (ellipsisb2) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(l,h)}$} (ellipsisc2);
        \draw (ellipsisb2) edge[out=-55,in=55,<-,thick] node [right] {\tiny$2\mu_{\NH}$} (ellipsisc2);

        \draw (bz) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(l,h)}$} (cz);
        \draw (bz) edge[out=-55,in=55,<-,thick] node [right] {\tiny$\mu_{\NH}$} (cz);
        % -----------------------------------------------
        % Fourth row--------------------------------------
        % -----------------------------------------------
        \node (da) at (0,-9) {$\vdots$};
        \node (db) at ($(da) + (3,0)$) {$\vdots$};
        \node (dc) at ($(db) + (3,0)$) {$\vdots$};
        \node (ellipsisd1) at ($(dc) + (3,0)$) {$\dots$};
        \node(dk) at ($(ellipsisd1) + (3,0)$) {$\vdots$};
        \node (ellipsisd2) at ($(dk) + (3,0)$) {$\dots$};
        \node(dz) at ($(ellipsisd2) + (3,0)$) {$\vdots$};
        % Transitions -----------------------------------
        % On Row:
        \draw (da) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(l,l)}$} (db);
        \draw (da) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$\mu_{\RG}$} (db);

        \draw (db) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(l,l)}$} (dc);
        \draw (db) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$2\mu_{\RG}$} (dc);

        \draw (dc) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(l,l)}$} (ellipsisd1);
        \draw (dc) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$333\mu_{\RG}$} (ellipsisd1);

        \draw (ellipsisd1) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(l,l)}$} (dk);
        \draw (ellipsisd1) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$K_{\RG}\mu_{\RG}$} (dk);

        \draw (dk) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(l,h)}$} (ellipsisd2);
        \draw (dk) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$(K_{\RG} + 1)\mu_{\RG}$} (ellipsisd2);

        \draw (ellipsisd2) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(l,h)}$} (dz);
        \draw (ellipsisd2) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$c_{\RG}\mu_{\RG}$} (dz);
        % With previous row:
        \draw (ca) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(l,l)}$} (da);
        \draw (ca) edge[out=-55,in=55,<-,thick] node [right] {\tiny$3\mu_{\NH}$} (da);

        \draw (cb) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(l,l)}$} (db);
        \draw (cb) edge[out=-55,in=55,<-,thick] node [right] {\tiny$3\mu_{\NH}$} (db);

        \draw (cc) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(l,l)}$} (dc);
        \draw (cc) edge[out=-55,in=55,<-,thick] node [right] {\tiny$3\mu_{\NH}$} (dc);

        \draw (ellipsisc1) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(l,l)}$} (ellipsisd1);
        \draw (ellipsisc1) edge[out=-55,in=55,<-,thick] node [right] {\tiny$3\mu_{\NH}$} (ellipsisd1);

        \draw (ck) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(l,h)}$} (dk);
        \draw (ck) edge[out=-55,in=55,<-,thick] node [right] {\tiny$3\mu_{\NH}$} (dk);

        \draw (ellipsisc2) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(l,h)}$} (ellipsisd2);
        \draw (ellipsisc2) edge[out=-55,in=55,<-,thick] node [right] {\tiny$3\mu_{\NH}$} (ellipsisd2);

        \draw (cz) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(l,h)}$} (dz);
        \draw (cz) edge[out=-55,in=55,<-,thick] node [right] {\tiny$\mu_{\NH}$} (dz);
        % -----------------------------------------------
        % Fifth row--------------------------------------
        % -----------------------------------------------
        \node (ea) [state] at (0,-12) {$(K_{\NH},0)$};
        \node (eb) [state] at ($(ea) + (3,0)$) {$(K_{\NH},1)$};
        \node (ec) [state] at ($(eb) + (3,0)$) {$(K_{\NH},2)$};
        \node (ellipsise1) at ($(ec) + (3,0)$) {$\dots$};
        \node(ek) [state] at ($(ellipsise1) + (3,0)$) {$(K_{\NH},K_{\RG})$};
        \node (ellipsise2) at ($(ek) + (3,0)$) {$\dots$};
        \node(ez) [state] at ($(ellipsise2) + (3,0)$) {$(K_{\NH},c_{\RG})$};
        % Transitions -----------------------------------
        % On Row:
        \draw (ea) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(h,l)}$} (eb);
        \draw (ea) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$\mu_{\RG}$} (eb);
